---
title: "STA130 Final Project"
author: "Larry Shi, Anthony Wong, Yan Zhang, Mike Wang"
output:
  ioslides_presentation:
  beamer_presentation: default
  widescreen: yes
subtitle: TUT 0206
editor_options:
  chunk_output_type: console
---

## Introduction

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Loading all dataframes
source('scripts/load_data.R')
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Drawing map
world <- map_data("world") 

iu <- internetusers_data %>% rename(region = Country) 

iu$region[4] <- "USA" # to match world map data

iu <- semi_join(iu, world, by = "region") #only keep countries according to world map data

# code below is modified from 
# https://stackoverflow.com/questions/29614972/ggplot-us-state-map-colors-are-fine-polygons-jagged-r
gg <- ggplot()

gg <- gg + geom_map(
  data = world,
  map = world,
  aes(x = long, y = lat, map_id = region),
  fill = "#ffffff",
  color = "#ffffff",
  size = 0.20
)

gg <- gg + geom_map(
  data = iu,
  map = world,
  aes(fill = `INTERNET USERS`, map_id = region),
  color = "#ffffff",
  size = 0.15
)

gg <- gg + scale_fill_continuous(low = 'thistle2', high = 'darkblue',
                                 guide = 'colorbar')
gg
```

--- 

- According to the map above, there is a huge difference in the distribution of internet users around the world. 
- What kind of factors are in play that create such a phenomenon? 
- Analyze the correlation between Internet users and 

  1. Population
  2. World Region
  3. Goverment's Expenditure on Health & Education 
  4. Economy & GDP
  5. Political System
  6. Family Income Distribution 
  
## Statistical Methods

From the initial analysis of the population data against internet user data, we found that:

  - Total population of a country doesn't really reflect the correlation between the two variables.
  - Created a new variable, `Percentage` = `INTERNET USERS` / `POPULATION`, reflects the percentage of the population that uses internet
  - Split `Percentage` into category of low, medium and high to allow us to classify internet users in terms of density.
  - Split the GDP into 5 categories: Above $40000, between \$40000 and \$21000, between \$21000 and \$11500, between \$11500 and \$3700, and below \$3700.
  
# Results

## Internet Users and Population 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('scripts/population.R')

top_internetusers_plot
```

## Internet Users and Population
```{r, echo=FALSE, message=FALSE, warning=FALSE}
top_internetusers_density_plot
```

## Internet Users and World Region
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('scripts/world_region.R')

region_total_internetuser_graph
```

## Internet Users and World Region
```{r, echo=FALSE, message=FALSE, warning=FALSE}
region_density_internetuser_graph
```

## Internet Users and Health
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('scripts/health.R')

lifeexpect_internet_graph
```

## Internet Users and Health
```{r, echo=FALSE, message=FALSE, warning=FALSE}
lifeexpect_internet_density_graph
```

## Internet Users and Health
Let $H_0$ be $\beta_1 = 0$ and $H_a$ be $\beta_1 \neq 0$

```{r, echo=FALSE, message=FALSE, warning=FALSE}
summary(lifeexpect_internet_model)$coefficients
```

Small p-value indicates strong evidence against the null hypothesis.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
summary(lifeexpect_internet_model)$r.squared
```

## Internet Users and GDP
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('scripts/gdp.R')

internetusers_gdp_graph
```

## Internet Users and GDP
```{r, echo=FALSE, message=FALSE, warning=FALSE}
internetusers_gdp_density_graph
```

## Internet Users and Education
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('scripts/education.R')
education_internet_graph
```

## Internet Users and Education
```{r, echo=FALSE, message=FALSE, warning=FALSE}
education_internet_density_graph
```

## Internet Users and Education

Let $H_0$ be $\beta_1 = 0$ and $H_a$ be $\beta_1 \neq 0$

```{r, echo=FALSE, message=FALSE, warning=FALSE}
education_internet_fit$coefficient
education_internet_fit$r.squared
```

## Internet Users and Democracy
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('scripts/democracy.R')
democracy_tree
```

## Internet Users and Democracy
```{r, echo=FALSE, message=FALSE, warning=FALSE}
tree_plot <- plot(as.party(tree), type = "simple", gp = gpar(cex = 0.5))
```

## Internet Users and Democracy
```{r, echo=FALSE, message=FALSE, warning=FALSE}
confusion_matrix 
accuracy
```

## Internet Users and Family Income Distributions
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('scripts/IncomeDistribution.R')
income_regression
```

## Internet Users and Family Income Distributions
```{r, echo=FALSE, message=FALSE, warning=FALSE}
mod_summary$coefficients
mod_summary$r.squared
```

## Conclusion (Population and World Region)

- <font size="4">The number of internet users seems to increase as the population increase.</font>
- <font size="4">However, some countries have significantly higher population than others causing inaccurate result.</font>
- <font size="4">% internet users is used instead showing there are not "real" correlation between population and internet users.</font>

<hr>

- <font size="4">Asia & Pacific region appeared to have most internet users due to its high total population.</font>
- <font size="4">A different graph plotted using % internet users shows that North America and Europe have much internet usage.</font>
- <font size="4">Both North America and Europe are mostly consistent with developed countries, while Asia, Africa and South America have many developing countries.</font>


## Conclusion (Life Expectancy and GDP)

- <font size="4">Initialial analysis showed that there is no correlation between life expectancy/GDP per person and the number of internet users.</font>
- <font size="4">Using % internet users, the plot shows a strong positive correlation between life expectancy and % internet users.</font>

<hr>

- <font size="4">Developed countries usually have better health care system resulting in higher life expectancy/GDP per person, and according to the world region analysis, this further shows that developed countries tends to have higher internet usage.</font>

<hr>

- <font size="4">Developed countries tends to have higher GDP per person which also result in higher % internet users, whereas developing countries with lower GDP per person have smaller % internet users.</font>
- <font size="4">Some developing countries that are making an effort to be a developed country (Countries have medium GDP, e.g. Brazil, Mexico ) have the large variation of internet users domestically. </font>


## Conclusion (Political System and Family Income)

- There exists a negative correlation between percentage of internet users and family income. Since the coefficient of determination is low, the linear model doesn't fit well and thus the data is non-linear
