---
title: "Project title"
author: "Team members names, tutorial section, and group number"
output:
  ioslides_presentation: default
  beamer_presentation: default
  widescreen: yes
subtitle: The subtitle of my project
editor_options:
  chunk_output_type: console
---


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)
```

# A Section Heading on its own page

## A heading that starts on a new page

This document shows a few basics on making slides with R markdown.

To produce the slides, Knit to HMTL (ioslides).

(You can also knit to PDF if you have LaTeX installed on your computer.)


---

Three dashes starts a new page when it is not started by a new header.

---

### This is a heading that doesn't start a new page

You can make text **bold** or in *italics*.

To make bullet points, start the points after a blank line:
 
- point one
- another point


---

Include some R output

```{r}
ggplot(cars, aes(x=speed, y=dist)) + geom_point()
```

---

Include the output without showing the code and R messages (which is what you want for your poster presentation).  This R code chunk also changes the size of the plot.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3}
ggplot(cars, aes(x=speed, y=dist)) + geom_point()
```

This plot shows that there is a positive relationship between distance and speed.

## Read more

There is more information on R markdown on the course website at [https://ntaback.github.io/UofT_STA130/Rmarkdownforclassreports.html](https://ntaback.github.io/UofT_STA130/Rmarkdownforclassreports.html)

For more on creating an `ioslides` presentation see [https://rmarkdown.rstudio.com/ioslides_presentation_format.html](https://rmarkdown.rstudio.com/ioslides_presentation_format.html)

# Headings you should include in your project

## Introduction

```{r, echo=FALSE}
# Loading all dataframes
source('scripts/load_data.R')
```

```{r}
# Drawing map
world <- map_data("world") 

iu <- internetusers_data %>% rename(region = Country) 

iu$region[4] <- "USA" # to match world map data

iu <- semi_join(iu, world, by = "region") #only keep countries according to world map data

# code below is modified from 
# https://stackoverflow.com/questions/29614972/ggplot-us-state-map-colors-are-fine-polygons-jagged-r
gg <- ggplot()

gg <- gg + geom_map(
  data = world,
  map = world,
  aes(x = long, y = lat, map_id = region),
  fill = "#ffffff",
  color = "#ffffff",
  size = 0.20
)

gg <- gg + geom_map(
  data = iu,
  map = world,
  aes(fill = `INTERNET USERS`, map_id = region),
  color = "#ffffff",
  size = 0.15
)

gg <- gg + scale_fill_continuous(low = 'thistle2', high = 'darkblue',
                                 guide = 'colorbar')
gg
```

Include here a few sentences to introduce the problem and provide context. You might want to briefly summarize the data in words (what is the data and what is it used for). You can present the questions you are investigating here. 


## Correlation Between Total Population and Internet Users
```{r, echo=FALSE}
source('scripts/population.R')

top_internetusers_plot
#top_population_plot
```

## Correlation Between GDP and Internet Users
```{r, echo=FALSE}
source('scripts/gdp.R')

internetusers_gdp_joint_graph
```

## Correlation Between Education and Internet Users
```{r, echo=FALSE}

```

## Correlation Between Democracy and Internet Users
```{r, echo=FALSE}
source('scripts/democracy.R')

democracy_tree

```

## Prediction of Density of Internet Users with Family Income Distributions
```{r, echo=FALSE}
source('scripts/IncomeDistribution.R')

income_regression

```

## Objectives (optional)

You can list the questions of interest in complete English sentences here to highlight them. 

```{r}

```

## Data Summary (optional)

Here you can explain how you cleaned the data and created variables suitable for answering your questions. 
You can also include graphical displays that either motivated or address the questions.

```{r}
  ## We are concerened with the relationship between the internet users and various factors such as gdp, education, and democracy. We joined the population table with the factors tables by country. This helps us compare the density of internet users in a country with each of the factors. 
```


## Statistical Methods

Describe here what you have done to the data without presenting any results (output). If you want to indicate variables by symbols or variable names, define them here. 

```{r}
  ##
```


## Results

Present the main results here, in order of importance, related to the questions asked. You might use tables or graphs, or other ways to summarize your results.

```{r}
  ##
```


## Conclusion

Give your main conclusions here. Follow the order of questions you presented. 

Here you can also mention any additional considerations, concerns, or issues you might have. For example, if the results were unexpected, you can discuss this and perhaps offer possible explanations.

```{r}
  ##
```


## Acknowledgements (optional)

If you received any help from someone other than your team members you can acknowledge them. For example:   
*The authors thank Wei for providing information on additional data resources. The authors would like to thank "TA name" for helpful suggestions and comments that improved the presentation of this poster.*



